Type theory in type theory with single substitutions

### 2024-09-17 types_2024_postproc/p.tex
stuff

TODO: beta equation for id, show what we can do with types in an open
context.

>>>>

Given a type $A:\Ty\,\diamond\,0$, and $a : \Tm\,\diamond\,A$, we have
\begin{alignat*}{10}
  & \lam\,(\lam\,\q)\cdot\cd\,A\cdot a && {=}(\Pi\beta) \\
  & (\lam\,\q[\langle\cd\,A\rangle])\cdot a && {=}(\lam[]) \\
  & (\lam\,(\q[\langle\cd\,A\rangle^+]))\cdot a && {=}([\q][^+]) \\
  & (\lam\,\q)\cdot a && {=}(\Pi\beta) \\
  & \q[\langle a\rangle] && {=}(\q[\langle\rangle]) \\
  & a
\end{alignat*}
If we want to specify open inputs $A':\Ty\,(\diamond\ext C)\,0$, and
$a' : \Tm\,(\diamond\ext C)\,A'$, we have to weaken our function to
accept them:
\begin{alignat*}{10}
  & \lam\,(\lam\,\q)[\p] : \Tm\,&& (\diamond\ext C)\,\\
  & && \Big(\Pi\,(\U\,0)\,\big(\Lift\,(\El\,\q)\Ra\Lift\,(\El\,\q)\big)[\p]\Big)
\end{alignat*}
But we have
\[
\lam\,(\lam\,\q)[\p] \overset{\lam[]\,2\text{x}}{=} \lam\,(\lam\,(\q[\p^{++}])) \overset{\q[^+]}{=} \lam\,(\lam\,\q)
\]
(with different implicit arguments), so we are able apply $\cd\,A'$
and $a'$ just as before. What we cannot do is to directly weaken a
term in context $\diamond$ to an arbitrary metavariable context
$\Gamma$, we can only do this step by step by applying weakening
$\blank[\p]$ for each type in the context.
